---
title: "Assignment 9"
author: "Steil"
date: "2023-01-30"
output: html_document
---

## Question 1
Using a for loop and an if statement, write a function to calculate the number of zeroes in a numeric vector. Before entering the loop, set up a vector of integers with some zero values. Then, set up a counter variable counter <- 0. Inside the loop, add 1 to counter each time you have a zero in the vector. Finally, use return(counter) for the output.

```{r}
vec <- round(runif(50))
counter <- 0

vec[2]

for(i in 1:length(vec)){
  if (vec[i]== 0) {
    counter <- counter+1} else
     {}
  print(counter)
}


```

## Question 2
Write a function that takes as input two integers representing the number of rows and columns in a matrix. The output is a matrix of these dimensions in which each element is the product of the row number x the column number.

```{r}
funktion <- function (x=4, y=5){
m <- matrix(nrow = x, ncol = y)
for (i in 1:nrow(m)){
  for(j in 1:ncol(m)){
   m[i,j] <- i * j
  }
}
return(m)
}
mat<-funktion(x=6, y=7)
mat

```


## Question 3
Use a for loop to repeat your previous functions from Weekly Assignment 2 (which simulate a data frame and extract a p-value) 100 times. Store the results in a data frame that has 1 column indicating the replicate number and 1 column for the p-values (a total of 2 columns and 100 rows).

```{r}
######################################
# FUNCTION: newFunk
# Input: means of the second column
# Output: Returns a data frame with a 'type' and 'value' column and 50 rows.

newFunk <- function(mean1 = 10, mean2 = 45){
  control = runif(25)
  treatment = runif(25)
  Type = c(control, treatment)
  data2 = rnorm(25, mean1, 1.5)
  data3 = rnorm(25, mean2, 2)
  Value = c(data2, data3)
  dFrame <- data.frame(Type, Value)
  return(dFrame)
}

output <- newFunk()
head(output)

#############################  
# Function: grilleMe
# Input: data frame with two columns
# Output: p-value of an ANOVA summary table


grilleMe <- function(ddFrame = output){
    # argument for ddFrame is NULL in the posted code
  yVar <- ddFrame[[1]]
  xVar <- ddFrame[[2]]
    # posted code skips defining these variables, just putting aov(Value ~ Test, data = df)
  aovtest <- aov(yVar ~ xVar, ddFrame)
  pValue <- summary(aovtest)[[1]][["Pr(>F)"]][1]
  return(pValue)
}

grilleMe()

####################
pValues <- data.frame()

for (i in 1:100){
  data1 <- newFunk() 
  data2 <- grilleMe(data1)
  goop <- data.frame(i, data2)
  pValues <- rbind(pValues, goop)
}

pValues

```

